Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System

### 2020-05-06 manuscript/manuscript.Rmd
dockerfile for dockerhub

```{r }
data_NPA <- gofer::data_NPA
data_SL <- gofer::data_SL
data_core <- gofer::data_core
data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
data_core$comparison <- sub("Iliac", "Iliac artery", data_core$comparison) 
data_core$comparison <- sub("Ax", "Axillary artery", data_core$comparison) 
data_core$comparison <- sub("Eso", "Esophageal", data_core$comparison)
data_core$patients <- sub("Gynecological Surgery", "Gynecology Surgery", data_core$patients)
data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)

@@

>>>>

```{r }
data_NPA <- gofer::data_NPA
data_SL <- gofer::data_SL
data_core <- gofer::data_core
data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study)

data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
data_core$comparison <- sub("Iliac", "Iliac artery", data_core$comparison) 
data_core$comparison <- sub("Ax", "Axillary artery", data_core$comparison) 
data_core$comparison <- sub("Eso", "Esophageal", data_core$comparison)
data_core$patients <- sub("Gynecological Surgery", "Gynecology Surgery", data_core$patients)
data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)

data_NPA_age <- gofer::data_NPA_age
data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study)

data_NPA <- data_NPA_age %>% 
  tidyr::pivot_wider(names_from = c(age_type, age_measure),
                    values_from = age) %>% 
  dplyr::rename(mean_age = mean_sd_average,
         lower_mean = mean_sd_lower,
         upper_mean = mean_sd_upper,
         median_age = median_iqr_average,
         lower_IQR = median_iqr_lower,
         upper_IQR = median_iqr_upper) %>% 
  left_join(data_NPA)

data_SL_age <- gofer::data_SL_age
data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study)

data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study)

data_SL <- data_SL_age %>% 
  tidyr::pivot_wider(names_from = c(age_type, age_measure),
                    values_from = age) %>% 
  dplyr::rename(mean_age = mean_sd_average,
         lower_mean = mean_sd_lower,
         upper_mean = mean_sd_upper,
         median_age = median_iqr_average,
         lower_IQR = median_iqr_lower,
         upper_IQR = median_iqr_upper) %>% 
  left_join(data_SL)

@@

ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "temp_range")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")
